\section{Introduction}
The positive effects of testing practices on production code quality have already been proven by a variety of studies e.g. \cite{laitenberger1998studying,binder1996testing}. Several different testing practices have been going around such as Test Driven Development \cite{erdogmus2010test}, Extreme Programming \cite{lindstrom2004extreme} or Acceptance Test-Driven Development \cite{aggarwal2014acceptance}. Some of which, e.g. Extreme Programming, involve a variety of different refactoring methods. Some refactoring methods described are specifically for test code \cite{van2001refactoring}. Our research deepens the knowledge on these test refactoring methods by shining light on the impact of refactoring test code on production code.

One should always take the related production code into consideration when refactoring the test code. Despite the fact that you might make the code more readable or maintainable, there is always a chance that the refactor might break the tests. Ofcourse not every refactor which is made on the test code is to improve the quality of the project, there are also test code refactors which are a result of changes which are made in the production code. Nonethless, each refactor could have an impact on the test code and researching this impact will allow us to determine the value of test code refactoring.

In order to keep the code readable and maintainable, the size of each of the classes should be kept to a minimum \cite{baggen2012standardized}. This way it is easier for the developer to understand what is happening in the code and when a method or class has to be refactored the impact on the code will be less significant. Beside the size of a class, the complexity also has an impact on the maintainability of the test code. Dealing with these problems can increase the quality of the test code and therefor increase the throughput and productivity of the development of a project \cite{athanasiou2011constructing}.

Despite the fact that keeping the size and complexity of a class to a minimum does have a positive effect on the project overall, in practice these methods are not always complied with. When a project becomes bigger it starts to get harder to keep it well structured. When the requirements of a project starts to differ, code changes have to be applied, however these code changes are often the reason why the maintainability or readability of the project starts to decrease. This is often because the developers do not realize what kind of impact refactoring test code can have on the maintainability of a project.

We decided to look at the way developers refactor their test code and if it does have a positive effect on the related production code. By examining the test code of multiple projects and evaluating the maintainability we can determine which of these refactor methods are used and if they do improve the maintainability of the production code. If the results of this research show that improving your test code by refactoring bad written code, we might stimulate developers to do this and improve the overall test code of a project.

During the evaluation of the multiple open-source projects we found out that during the development of a project, the test code does get refactored a lot. However, only a small fraction of these refactors was to actually improve the maintainability of the code. In this paper we will explain how we analyzed these repositories and which results came out of this evaluation.
\newpage